---
title: "World Happiness Analysis"
author: "Danlu Pan"
date: "December 4, 2017"
runtime: shiny
output: slidy_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
<br>
<br>
<center>Catalogue<center>
<br>
<br>
<center>**Overview**<br />
Metrics relation<br />
Economy & Ranking<br /> 
World Happiness Map<br />
<br>
**Dig into Estern Asia**<br />
Metrixs in Estern Asia<br />
Health condition in Estern Asia<center>


***


```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
##Three packages involved
library(ggplot2)
library(dplyr)
library(corrplot)
```


```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
# read world happiness data
world_happiness1 <- read.csv("2015-4.csv")
```

```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
str(world_happiness1)
```


```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}

#clean data frame
world_happiness<-select(world_happiness1,
                  year,
                   Country, 
                   Region,
                   Happiness=Happiness.Score,
                   Rank=Happiness.Rank,
                   Economy=Economy..GDP.per.Capita.,
                   Family,
                   Health=Health..Life.Expectancy.,
                   Freedom,
                   Trust=Trust..Government.Corruption.,
                   Generosity,
                   Dystopia.Residual)
```


```{r  echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
#Check for missing values
sapply(world_happiness, function(x) sum(is.na(x)))
## There is no missing data. 
```
```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
#Check the class of each matrix
sapply(world_happiness, function(x) class(x))
```

```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}

#boxplot(world_happiness$Happiness,data=world_happiness, xlab="boxplot of Happiness")
#boxplot(world_happiness$Economy,data=world_happiness, xlab="boxplot of Economy")
#boxplot(world_happiness$Family,data=world_happiness, xlab="boxplot of Family")
#boxplot(world_happiness$Family,data=world_happiness, xlab="boxplot of Freedom")
#boxplot(world_happiness$Health,data=world_happiness, xlab="boxplot of Health")
#boxplot(world_happiness$Trust,data=world_happiness, xlab="boxplot of Trust")
#boxplot(world_happiness$Generosity,data=world_happiness, xlab="boxplot of Generosity")
#boxplot(world_happiness$Dystopia.Residual,data=world_happiness, xlab="boxplot of Dystopia.Residual")
#A few outliers are found, 
 #  in order to maintain whole data  information,
 #  decided to keep them 

```

<br>
<br>
<center>Overview<br />
<br>
<br>
[1] Metrics relation
```{r echo=FALSE, cache=FALSE,results = 'hide'}
#find all numeric variables
world_happiness2<-select(world_happiness,-year,-Rank)
isnumeric <-sapply(world_happiness2, function(x) is.numeric(x))
```
```{r echo=FALSE,warning=FALSE,fig.width=7,fig.height=7,fig.align="center"}
#create a correlation plot
cor_happiness<-cor(world_happiness2[,isnumeric])
colnames(cor_happiness)<-c("H","E","F","H","F","T","G","D")
corrplot(cor_happiness, align="c",method="color",tl.pos = "lt", tl.col = "black", tl.offset=1, tl.srt = 0)
```


***
<br>
<br>

```{r echo=FALSE, cache=FALSE,results = 'hide'}
# convert data to a percentage data frame
percent_factor <-world_happiness %>%
  group_by(year)%>%
  summarize(percent_Economy=sum(Economy)/sum(Happiness)*100,
            percent_Family=sum(Family)/sum(Happiness)*100,
            percent_Health=sum(Health)/sum(Happiness)*100,
            percent_Freedom=sum(Freedom)/sum(Happiness)*100,
            percent_Trust=sum(Trust)/sum(Happiness)*100,
            percent_Generosity=sum(Generosity)/sum(Happiness)*100,
            percent_Dystopia.Residual=sum(Dystopia.Residual)/sum(Happiness)*100)
```

```{r echo=FALSE,cache=FALSE,results = 'hide'}
#create a table for pie chart
percent <- data_frame(Factor=c("Economy","family","Health", "Freedom","Trust", "Generosity","Dystopia.Residual"),
           Percent=c(15.74,18.43,11.72,7.97,2.67,4.41,39.06))
```
```{r echo=FALSE,fig.width=6,fig.height=4,fig.align="center"}
# plot a pie chart to show contribution of each factor to world happiness
pieplot<- ggplot(percent, aes(x ="",y=Percent,fill=Factor))+geom_bar(stat = "identity")+coord_polar(theta="y")+scale_fill_brewer(palette="Blues")
#add labels and titles
pieplot + labs(y="Percent %", title="Metrix contributions to world happniess")+theme(plot.title = element_text(face="bold",hjust=0.5))+geom_text(aes(label=Percent),col="black",position=position_stack(vjust = 0.6))
```

***
<br>
<br>
[2]Focus on relation between happiness ranking with **economy** condition worldwide 
```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
# create table related to the world happiness data of economy
Economy <-select(world_happiness,Economy,Country,Rank,Economy,year)
Economy <- arrange(Economy,Rank)
```

```{r echo=FALSE,fig.width=6,fig.height=4,fig.align="center"}
# plot the relation between happiness ranking with economy condition by year
plot1<- ggplot(Economy,aes(x=Rank,y=Economy,fill=Economy,col=factor(year)))+geom_line()+facet_wrap(~year)
# add titles an labels
plot1+labs(title="Economy & Ranking worldwilde",color="year")+theme(plot.title = element_text(face="bold",hjust=0.5))

```

* We can tell that there is a positive trend related with economy and happiness ranking. 

***
<br>
<br>
[3]focus on showing a **map of world happiness** all ove the world 
```{r echo=FALSE}
shinyApp(
  ui = fluidPage(    
  
  # Give the page a title
  titlePanel("Map of world happiness"),
  
  # Generate a row with a sidebar
  sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("year", "year:", 
                  choices=c("2015","2016","2017")),
      hr(),
      helpText("year:2015-2017")
    ),
    
    # Create a spot for the map
    mainPanel(
      plotOutput("conditionPlot")  
    ))),
  
server = function(input, output) {
  
  # Fill in the spot we created for a plot
  output$conditionPlot <- renderPlot({
    map_data <- world_happiness %>%
    filter(year==input$year)%>%
    select(-year,-Region)
    # use map_data to convert data into maps
    map_world <- map_data(map="world")

    # since values in Country and Region not match, try to merge them
    map_world$Country <- map_world$region
    map_world_after <- merge(map_world, map_data, by="Country", all.x=TRUE)

    # reorder world map data
    map_world_after <- map_world_after[order(map_world_after$group, map_world_after$order), ]
    # create world map of happiness
Happiness.plot <- ggplot() + geom_map(data=map_world_after, aes(map_id=region, x=long,  y=lat,fill=Happiness),map=map_world_after)

# add color, adjust coordinate and add ttile & theme 
Happiness.plot <- Happiness.plot + scale_fill_gradient(low = "white", high = "blue", guide = "colourbar")+coord_equal()+labs(x="Latitude",y="Longitude")+ggtitle(label = "World Happiness Map 2016")+theme(plot.title = element_text(face="bold",hjust = 0.5)) 
Happiness.plot
  })
  },
  options = list(height = 600,width=900)
)
```

***
<br>
<br>
<center>**Focus on happiness scores in Eastern Asina**<center>
```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
# filter rows of Eastern Asia
Asia <-filter(world_happiness,Region=="Eastern Asia")
```
```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
# create a table related to the world happiness data of Eastern Asia
by_year_country<-Asia %>%
  group_by(year,Country) %>%
  summarize(Rank,Economy, Health)
```
```{r echo=FALSE, cache=FALSE,results = 'hide',message=FALSE,warning=FALSE}
# range dataframe to prepare for shiny app
Asia2015 <-filter(Asia, year==2015)
condition2015 <- as.matrix(select(Asia2015, -year,-Region,-Country,-Rank))
rownames(condition2015) <- Asia2015$Country
```

[1]To show value change of each metrix in different part of Eastern Asia  

```{r echo=FALSE}
shinyApp(
  ui = fluidPage(    
  
  # Give the page a title
  titlePanel("Condition of Eastern Asia in 2015"),
  
  # Generate a row with a sidebar
  sidebarLayout(      
    
    # Define the sidebar with one input
    sidebarPanel(
      selectInput("Condition", "Condition:", 
                  choices=colnames(condition2015)),
      hr(),
      helpText("different metrixs to evaluate world happiness in Eastern Asia, 2015")
    ),
    
    # Create a spot for the barplot
    mainPanel(
      plotOutput("conditionPlot")  
    ))),
  
server = function(input, output) {
  
  # Fill in the spot we created for a plot
  output$conditionPlot <- renderPlot({
    
    # Render a barplot
    barplot(condition2015[,input$Condition], 
            main=input$Condition,
            col=c("indianred", "orange", "gold","skyblue4","light blue","blue"),
            ylab="condition name",
            xlab="Year 2015")
  })
  },
  options = list(height = 600,width=900)
)
```

***

<br>
<br>
<br>
[2]Focus on relation between happiness ranking with **health** in **Eastern Asia**

```{r echo=FALSE,cache=FALSE,warning=FALSE,fig.width=10,fig.height=4,fig.align="center"}

#plot the relation between happiness ranking with health condition by year
by_year_country <- arrange(by_year_country,Rank)
healthplot <- ggplot(by_year_country,aes(x=reorder(Country,Rank),y=Rank,fill=Health))+labs(x="Countries in Easatern Asia")+geom_histogram(stat = "identity")+facet_wrap(~year)
# add titles and labels
healthplot+labs(title="Health condition & Ranking in Estern Asia")+theme(plot.title = element_text(face="bold",hjust=0.5))
```

* We can tell that health condition is not exactly positively related  to happiness ranking.

***